Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-23 RNARedPrint.tex
correction

Since $\F$ defines potentially more complex dependencies, which can
relate more than two positions, its dependencies cannot be similarily represented by a
graph. Instead, this requires a structure known as \Def{hypergraph}, which
consists of vertices (here, the sequence positions) connected by
\Def{hyperedges} are sets of vertices---in generalization of graphs, where edges are pairs of vertices.
%Undirected graphs can be
%modeled as hypergraphs whose hyperedges are pairs of vertices, but
%hypergraphs also allow to express complex dependencies.

>>>>

Since $\F$ defines potentially more complex dependencies, which can
relate more than two positions, its dependencies cannot be similarily
represented by a graph. Instead, this requires a structure known as
\Def{hypergraph}, which consists of vertices (here, the sequence
positions) connected by \Def{hyperedges}, which are sets of
vertices. In this way, hypergraphs generalize undirected graphs, where
edges are sets of two vertices.
%Undirected graphs can be
%modeled as hypergraphs whose hyperedges are pairs of vertices, but
%hypergraphs also allow to express complex dependencies.
